% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large SPC Matthew Levandowski}  & 315-286-2383\\
10897 48th Ave &  levandowski.matthew@gmail.com \\
Allendale, MI 49401-8142 & http://www2.gvsu.edu/\textasciitilde levandma/\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Objective}

Experienced military leader with documented success in responsible and challenging positions; seeking a position to gain work related experience in order to progress to higher level positions. I have a proven record of accomplishment, mission-critical decision making, time-management, and extensive teamwork abilities; with the ability to develop and implement effective action plans. I have fulfilled a tour of duty in Afghanistan and four years of military service with an honorable discharge.


\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Grand Valley State University}{Allendale, MI}{B.A.Sc., Information Systems (Grades: 80\%)}{Sep. 2009 - Present}
	\begin{itemize}
		\resitem{Relevant courses: Java programming, Data Structures and Algorithms, Digital Design, Computer Architecture}
	\end{itemize}

\item
	\ressubheading{Muskegon Community College}{Muskegon, MI}{A.S.A., Science and Arts }{2001-2006}
	\begin{itemize}
		\resitem{Finished degree after completing 4 year Active Duty contract with the U.S. Army.}
		\resitem{Relevant courses: Physics, Calculus, Statistics, Electroacoustic music}
	\end{itemize}

\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{180th Transportation Co., U.S. Army Reserve}{Muskegon, MI}{25F Communication Specialist}{Aug 2009 - Aug. 2010}
	\begin{itemize}
		\resitem{Train on various soldier skills and wheeled truck driving. Plan and execute regular training exercises in support of the 180th Transportation Company.}
	\end{itemize}

\item 
	\ressubheading{Kohls Department Store}{Muskegon, MI}{Advertisement Setter}{Nov 2009 - Present}
	\begin{itemize}
		\resitem{Work with other associates as a team to inventory and assess advertisement pricing and policies for entire store. Assist customers and perform customer service tasks.}
	\end{itemize}

\item
	\ressubheading{Shareco Communications}{Grand Rapids, MI}{Telecommunications Line Installer}{Mar. 2008 - Nov. 2008}
	\begin{itemize}
		\resitem{I was responsible for the installation, repair, and termination of cabling in commercial and residential business.}
		\resitem{Proficient in the use of  CAT5E, CAT6, 100-pair copper wire, and standard RG5 coaxial cable.}
		\resitem{Installation and splicing of fiber optic lines in commercial settings.}
	\end{itemize}

\item
	\ressubheading{710 BSB, 3rd BCT, 10th MTN DIV, U.S. Army}{Afghanistan}{Communications Specialist OEF VII}{Feb. 2006 - Jul. 2007}
	\begin{itemize}
		\resitem{Deployed in support of Operation Enduring Freedom as a communication specialist for a company sized element with more than 150 employees. }
		\resitem{Participated in the Joint Task Force as security for the occupying NATO and ISAF forces.}
		\resitem{Participated in the successful repatriation of a US Soldier in a Search and Rescue Mission.}
		\resitem{Maintained and Installed radio communication and navigation devices in armored vehicles.}
	\end{itemize}

\item
	\ressubheading{10th Mountain Division, U.S. Army}{Fort Drum, NY}{25F Network Switching Systems Operator / Maintainer }{Aug. 2005 - Feb. 2006}
	\begin{itemize}
		\resitem{Directly responsible for the installation, maintenance, and repair of over half a million dollars of communication equipment for a company with over 150 soldiers.}
		\resitem{Participated in successful training at JROTC in Fort Polk, Louisiana.}
		\resitem{Conducted numerous training exercises successfully in light infantry.}
	\end{itemize}
\end{itemize}

\resheading{Military Awards}
	\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		Joint Service Achievement Medal (Secretary of Defense) & May 2007\\
		ISAF Medal Afghanistan (NATO) & 2007\\
		Joint Meritorious Unit Award (CJTF-76) & 2007\\
		Army Commendation Medal (U.S. Army) & 2007\\
		Army Good Conduct Medal (x2) (U.S. Army) & 2007\\
		Army Certification of Achievement (U.S. Army) & 2006\\
\end{tabular*}

\resheading{Security Clearance}
	\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		Secret (US Army) & Exp. 2012 \\
\end{tabular*}

\resheading{Skills}

\begin{description}
\item[Programming:]
Java, HTML, CSS, BASH, Perl
\item[Operating Systems:]
Linux (Debian, Gentoo, ArchLinux), Solaris, UNIX, Windows 95/98/NT/2000/XP/VISTA/WIN 7
\item[Applications:]
Vim, Eclipse, \LaTeX, OpenOffice, MS Office 2007, Adobe Photoshop/Premiere
\item[Military Skills:]
General Dynamics C4 - MSE Network Systems, COMTECH MTS, Plugr, and BlueForce Tracker GPS devices, COMSEC devices, SIPR and NIPR networks, SINCGARS Radios, SMART-T Satellite Communications, Cisco routers
\item[Miscellaneous:]
software configuration management, strong verbal and written communication skills, excellent troubleshooting skills, exceptional problem solving skills, good teams skills
\end{description}

\resheading{Interests}

\begin{description}
\item[Academic:] RF/wireless, Operating Systems design / maintenance, Computer Security, Information Assurance
\item[Sports:] Playing soccer and Running
\item[Computers:] Enjoy using and learning Linux systems, Repairing computers and electronics at home and for friends, and writing JAVA software
\item[Musical:] Playing guitar and midi keyboard
\item[Memberships:] Student Veteran Organization, CS Study Group, Total Trek Quest
\item[Other:] Reading novels
\end{description}

\end{document}
